Can machine learning correct microwave humidity radiances for the influence of clouds?

### 2021-03-10 Article/Review_1/response_reviewer_1.tex

The authors would like to thank the reviewer for his/her careful review and constructive comments, which we believe will help improve the content of the manuscript.  Below, under each bullet point, we provide a point by point response to each comment/question. The author responses are given in blue, and textual changes are italicised.

\section*{General comments}

\begin{itemize}

\item 	``precipitation and most dense clouds'' I think the hydrometeor size is an important factor.\\

@@

\textcolor{blue}{Reply: We agree that the hydrometeor size is an important aspect, but when it comes to an overview of the cloud contamination at 183\,GHz, precipitating clouds and clouds with large optical thickness have the strongest effect, and a dense cloud could be composed of hydrometeors of different shapes and sizes. }\\

\item	L66: ``only using measurements (no background data involved)'' My understanding is
		that the method is in theory model-free, but for the demonstration in this study, simulations (e.g. background simulated at MWHS2 frequency) are used. Am I correct?
		Maybe this should be stressed here. Why not try with real MWHS2 observation for the
		all sky dataset?\\

\textcolor{blue}{Reply: Yes, the demonstration of the entire concept is based on simulations. We do not try with the real MWHS-2 observations as the validation of the training process could only be performed against clear-sy simulations. To stress on the fact that only background MWHS-2 observations are used, we have added the following text to Sect. 2.1.1:\\
Pg 4, line 104:
``\textit{For the demonstration of the study, MWHS-2 simulations from the ECMWF model background are used. Actual measurements are not taken into account. The requisite data was obtained from ECMWF. More details are described in Sect.2.1.1}.''} \\

@@

\item	
		L159: "for all selected quantile fractions " by quantile fraction, do you mean the n th
		amongst the 7 selected (from 0.2 to 99.8\%)? Also, 16, 50 and 85\% are not symmetric
		(rounding?)\\

\textcolor{blue}{Reply: Yes, the selected quantiles are the seven percentiles mentioned. We re-phrase some sentences here to make it more clear. 85\% is a typo, it should be 84\%. It has been corrected.}\\

\item	
		L163: Pfreundschuh uses an indicator function I (=1 or 0) in the CRPS, the authors
		here use y, can they explain the difference?\\

\textcolor{blue}{Reply: The CRPS in the manuscript is incorrect. We thank the reviewer for highlighting it. We have corrected the equation in the revised manuscript.}\\

@@

\item	L460: "but such information would be not be completely orthogonal" duplicate "be"

\textcolor{blue}{Reply: The duplicate word is removed. }\\

\item	
		Table 1: NEDT are constructor specifications, the real noise is lower, see
		Fig 5 Guo, Y., J. Y. He, S. Y. Gu, and N. M. Lu, 2019: Calibration and validation of
		Feng Yun-3-D microwave humidity sounder II. \\
		IEEE Geoscience and Remote Sensing
		Letters, doi:10.1109/LGRS.2019.2957403.
		Tab 5 Carminati, F., Atkinson, N., Candy, B., Lu, Q.: Insights into the Microwave Instruments Onboard the Feng-Yun 3D Satellite: Data Quality and Assimilation in the Met Office NWP System. Adv. Atmos. Sci. (2020). https://doi.org/10.1007/s00376-020-0010-1 \\

\textcolor{blue}{Reply: The reviewer rightly mentions that the real noise is lower, however we add the sensor noise according to the pre-launch specifications. This can be viewed as a conservative estimate of the sensor noise to include other sources of error not accounted for in NEDT. For example in the study by \citet{Carminati-fy3d-2020} the authors describe radiation leak affecting the higher frequency channels.\\
We clarify in the manuscript that pre-launch specification values are used.}

@@

\end{itemize}

\section*{Questions}
\begin{itemize}

\item	
		Is this method applicable to IR e.g. to an ATOVS system?\\

\textcolor{blue}{Reply:  Yes, the method could potentially be applied to IR. The operation and  performance of the cloud correction approach is based on the fact that different frequencies have varying sensitivity to cloud signatures in the same field of view. For IR, infact this feature is regularly used to flag out cloud contamination. Most cloud flagging schemes for IR are based on brightness temperature thresholds. \\
In the manuscript, without going into the details, we mention that ``\textit{The scheme could also be potentially extended to cloud correction at infra-red frequencies}''
}\\

@@

\item 		
		The authors explain that it could benefit the all-sky assimilation systems indirectly for
		the analysis increment. Instead (or in addition) could it be used to model the variable
		observation error (when and by how much to be inflated)? This would be, in my view,
		the most valuable.	\\

\textcolor{blue}{Reply: The reviewer has a very good point. At ECMWF, the observational errors for MHS and MWHS-2 are defined as quadratic functions of symmetric cloud indicator \citep{geer2015scatteringindex}. The observational errors are higher in regions for cloud and vice-versa. Thus it could be potentially feasible to use the QRNN identified cloud impact to formulate the observational errors.  This could probably be the best use of the QRNN technique for all-sky. Of course using QRNN to develop a full observational model, would require to characterize the performance of the scheme over upper latitudes, land and ocean.\\
We have included the following text in the manuscript:\\
Pg 29, Line 577: ``\textit{Also, it could be feasible to use the QRNN identified cloud impact to formulate the observational errors. This may be the best use of the QRNN technique when it comes to all-sky assimilation.}''}\\

@@

\item	Could the uncertainty use for weak constraint 4dvar?\\

\textcolor{blue}{Reply: Although, the uncertainties obtained from QRNN do not have a direct application to weak constraint 4dvar, but they could still be considered as a diagnostic to help evaluate the weak constraint in the troposphere. For example, undiagnosed cirrus contamination in the upper troposphere might be associated with apparent model biases that are actually caused by systematic forward model errors. }\\

\item	
		What is the resource cost of this method (is this fast enough to be used in 1-h regional
		nwp with 30min window)?\\

\textcolor{blue}{Reply: The method is probably computationally more complex than other methods
	based on, for example, a scattering index, we consider it unlikely that the
	computational cost of the scheme would be an issue in an operational context.\\
	The only demanding part of the scheme is the training process, but it is performed offline. Evaluating the network during operational processing  would require only a forward pass through the network. In the study, we employ a simple, fully-connected network architecture so that 	the complexity of a forward pass is dominated by a low number of matrix-vector multiplications (one for each layer the network). The matrix-vector
	multiplications are typically combined into matrix-matrix multiplications to
	evaluate the network for multiple observations in parallel. Due to the recent
	popularity of neural networks, highly optimized implementations of these methods
	are available for all common computing architectures. 
	We have included the following information in the Conclusions section.
Pg 29, Line 591: ``\textit{Due to its low computational cost, implementation of this scheme should be feasible in NWP models given their computational constraints. Although the method is probably computationally more complex than existing cloud clearing methods, the demanding part of the scheme, the training, is performed offline. The operational processing only requires a forward pass through the neural network, for which highly-optimized implementations are readily available on all common computing platforms.}''}	
\end{itemize}

### 2021-03-10 Article/ici_submm_cloudcorr_v1.1.tex
version submitted final upload

In this study, we approach the cloud filtering task from a new angle. The basic idea
is to derive an estimate of the corresponding noise-free clear-sky (NFCS) value
(i.e.\ the radiance that would have been measured in absence of noise and
hydrometeors). Not only a best estimate is provided, but also a case-specific uncertainty. This information could be used as a pure filter, by rejecting data where the correction exceeds some threshold value. However, even better is to replace the original value with the predicted NFCS value when forming the clear-sky dataset. We denote this approach as cloud correction. This is done for each channel separately and by only using the measurements, although the scheme is demonstrated in the study by using simulated observations. It is shown below that a basically bias free cloud correction can be obtained. This feature also removes the need for defining threshold values, as long as the retrieval or assimilation system can incorporate the uncertainty of the corrected value. As also will be shown, the uncertainty for originally clear-sky data is determined
by noise, but the uncertainty increases with magnitude of correction.
Accordingly, the cloud correction approach permits the full weight of
clear-sky data to be preserved.

@@

The main focus of this study is the potential of this cloud-correction
method using sub-millimetre (sub-mm) observations, which will become available
operationally with the launch of the Ice Cloud Imager \citep[ICI,][]{eriksson:towar:20} on board the next generation of European Organisation for the Exploitation of Meteorological Satellites Polar System - Second Generation (EUMETSAT EPS-SG). Additionally, we demonstrate the feasibility of the approach based on 89 and 150\ GHz channels \citep[following][]{geer2015scatteringindex}, which are available on several sensors extant today. The focus
on sub-mm channels is motivated by several reasons. First, the higher
frequencies are more sensitive to scattering effects from smaller
hydrometeors and are thus expected to provide greater sensitivity to high altitude cirrus clouds. For example, in some cloudy situations the
cloud impact at 183\,GHz may be of the order of thermal noise and modelling uncertainties,
while the impact at 325\,GHz is significant enough to provide sufficient signal to noise for identifying cloud. Second, the proposed
cloud correction methods allow integration of ICI sub-mm observations in
clear-sky DA schemes with no further modifications, thus providing a simple
way to make use this novel data source as soon as it becomes available.

@@

\section{Data and methods}
\label{data_methods}
%
\subsection{Satellite Instruments}
%
\subsubsection{ MicroWave Humidity Sounder-2}
%
%t
\begin{table}[t]
	\caption{Specifications of MWHS-2 channels relevant to this study.}
	\label{tab:specifications_MWHS2}	
	\begin{tabular}{crrr}
		\tophline
		Channel & Frequency 	& Bandwidth & NE$\Delta$T \\
		& [GHz]			& [MHz]		& [K]		\\
		\middlehline
		1	&	89.0   		  & 1500			&	1.0	\\
		6	&	118.75±1.1    & \phantom{0}200 	&	1.6\\
		7	&	118.75±2.5    & \phantom{0}200 	&	1.6\\
		10	&	150.0         & 1500 			&	1.0 \\
		11	&	183.31±1.0      & \phantom{0}500  &	1.0 \\
		12  & 	183.31±1.8    & \phantom{0}700 	&   1.0\\
		13  & 	183.31±3.0      & 1000    		&	1.0	\\
		14  & 	183.31±4.5    & 2000    		&	1.0\\
		15  & 	183.31±7.0      & 2000  			&	1.0  \\
		\bottomhline
	\end{tabular}
	\belowtable{} % Table Footnotes
\end{table}
The MicroWave Humidity Sounder 2 (MWHS-2) is an instrument on two current satellites in the FengYun-3 series, FY-3C and FY-3D. MWHS-2 is a cross track scanning microwave radiometer and measures 15 frequencies in the range 89--191\,GHz. 89\,GHz and 150\,GHz are window channels, five humidity sounding channels are centered around 183\,GHz, and eight temperature sounding channels are centered on the 118\,GHz oxygen absorption line. The five humidity sounding channels are similar to ATMS. Observations from MWHS-2 are routinely assimilated in all-sky conditions at the European Centre for Medium-Range Weather Forecasts (ECMWF) with demonstrable positive impact on forecast performance \citep{duncan2020MWHS}.

For the demonstration of the study, MWHS-2 background observations or simulations are used. Actual measurements are not taken into account. The requisite data was obtained from ECMWF. More details are described in Sect.~\ref{simulations}.

@@

\subsection{Simulations}
%
\begin{figure}[t]
	\centering
	\includegraphics[width = 70mm]{Figures/fig00.pdf} 
	\caption{Probability distribution functions (PDFs) of simulated and observed brightness temperatures for MWHS-2 channel 14. The data covers latitude range $60^{\degree}$\,S to $60^{\degree}$\,N, and satellite zenith angle less than $7.5^{\degree}$.}
	\label{fig:distribution_OB_mwhs14}	
\end{figure}
\label{simulations}
MWHS-2 simulated radiances during the period June--July 2020 are sourced from ECMWF. In the current version of the ECMWF Integrated Forecasting System (IFS), cycle 47R1 \citep{IFS47R1chap1}, clear-sky and all-sky radiative transfer are performed simultaneously for monitoring purposes, despite all humidity sounders being assimilated via all-sky exclusively. These side by side radiative transfer calculations on a large variety of model scenes provides an ideal dataset for comparing radiances with and without cloud effects. Out of all the available observations during the period, we use data for the latitudinal range: $60^{\degree}$\,S to $60^{\degree}$\,N and satellite zenith angle, less than $7.5^{\degree}$. With this filter, we have approximately 290\,000 cases. Figure~\ref{fig:distribution_OB_mwhs14} shows the histogram of background and bias corrected observations for MWHS-2 channel 14. The part of the distribution matching clear-sky conditions shows a good agreement between the background and the observations. The main deviations in the distributions arise from the hydrometeor scattering. With limited scope of particle size and shape variation in current NWP microphysical schemes, the true cloud variability cannot be  described accurately, and a bias correction is necessary to be closer to reality.

@@

The simulations are split into training and testing datasets. The training dataset is used to train the machine learning model, while the testing dataset is used to evaluate the trained model. The construction and details of the model are described in Sect.~\ref{sec:QRNN}. For MWHS-2, 220\,000 simulations are randomly selected as training dataset, while 70\,000 are used for testing. For ICI, 175\,000 cases are randomly picked to form the training set. The remaining 45\,000 are used for testing. A smaller database is selected for SMS. 120\,000 simulations are used for training and the remaining 23\,000 for testing.

@@

QRNN's are trained to minimize the mean of the sum of the quantile loss functions,
%
\begin{align}
\mathcal{L}_\tau(y_\tau, y) &=
\begin{cases}
\tau|y - y_\tau|, & y_\tau < y \\ (1 - \tau)|y_\tau - y|, & \text{otherwise}
\\
\end{cases}
\end{align}
%
for all selected quantile fractions, where $y_\tau$ is the predicted
quantile and $y$ the reference value from the training or test data. The
quantile loss is also used in this study as a performance criterion for the tuning of
the hyper-parameters of the QRNN (see Appendix~\ref{appendix:hyperparamter}). In
addition to the quantile loss, also the Continuously Ranked Probability Score
(CRPS) is considered. Given a predicted CDF
$F$ and the reference value $y$, the CRPS is defined as
%
\begin{align}
\text{CRPS}(F, y) = \int_{-\infty}^{\infty} \left (F(y') - y\right )^2\: dy'.
\end{align}
%
To compute the CRPS for a prediction from a QRNN, the predicted quantiles are
used to derive a piece-wise linear approximation of the CDF of the predicted
distribution. Note that CRPS is only used to evaluate hyper-parameter tuning.

@@

\subsection{Evaluation metrics}
\label{sec:validation}
\begin{figure}[t]
	\centering
	\includegraphics[height=70mm]{Figures/fig01.pdf} 
	\caption{Examples showing the predicted quantiles of the conditional distribution of $\ynfcs$ }
	\label{fig:posterior_distribution_I1V}	
\end{figure}
QRNN predictions are posterior probability distribution of $\ynfcs$ described over the chosen quantiles. In order to facilitate the interpretation of results, examples of QRNN outputs are shown in Fig.~\ref{fig:posterior_distribution_I1V}. These examples illustrate the predicted quantiles for three different cases. The quantiles provide a quantification of the prediction uncertainty through a probabilistic upper and lower bound for each case. This is in contrast with other conventional correction/filtering methods, which give out only point estimates. However, for most applications only a single point estimate is required. In Bayesian analysis, usually the posterior mean or posterior median are selected as point estimates. In this study, we chose the posterior median as the best estimate for $\ynfcs$. To analyse the ability of QRNN in correctly predicting the point estimate, deviation of the median value from the corresponding true value ($\yonfcs$) is evaluated using common performance indicators like bias, mean absolute error (MAE) and standard deviation (STD). The asymmetry of error distributions around their mean is also calculated through the measure of skewness. For a univariate dataset of length $N$, the Fisher-Pearson coefficient of skewness is defined as: 
\begin{equation}
g_1 = 	\frac{\sqrt{N(N-1)}}{N-2} \frac{\sum_{i = 1}^{N}(Y_i - \bar{Y})^3/N}{\sigma^3} \,,
\end{equation}
where $\bar{Y}$ and $\sigma$ are mean and standard deviation of the deviations, respectively.

@@

\subsubsection{QRNN-single applied to MWHS-2 channel 14} 
\begin{figure}[t]
	\centering
	\includegraphics[width = 70mm]{Figures/fig02.pdf} 
	\caption{The distribution of point estimates (``Predicted'') obtained from QRNN-single 89+150\,GHz for MWHS-2 channel 14. The corresponding distributions for all-sky and clear-sky simulations are also shown.}
	\label{fig:distribution_predicted_mwhs14}	
\end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width = 70mm]{Figures/fig03.pdf} 
	\caption{The error distribution for deviations of point estimates from NFCS simulations. The results are from QRNN-single experiment 89+150\,GHz and MWHS-2 channel 14. Noise is also plotted for reference. The label ``All-sky'' represents the all-sky simulations, ``Predicted (All)'' denotes the predicted point estimates. The error distribution achieved with scattering index (SI) filtering is also shown (Filtered (SI)). }
	\label{fig:error_distribution_mwhs14}	
\end{figure}
\begin{table*}[t]
	\caption{The error statistics for deviations of point estimates from NFCS simulations. Results are for different QRNN experiments for MWHS-2 channel 14 (see Sect.~\ref{sec:QRNN_expt_MWHS}). The statistics for all-sky and clear-sky simulations are also provided. The label ``All'' denotes the entire dataset of predicted point estimates, while ``Pred. (5\,K)'' refers to the predicted point estimates but where cases with cloud correction greater than 5\,K are excluded. The last two columns show the statistics obtained after filtering cloudy cases according to scattering index (SI) and scheme by \citet{buehler:aclou:07} (B183). Bias, MAE, STD are in K, skewness is dimensionless.}
	\label{tab:error_statistics_mwhs_14}
	\setlength{\tabcolsep}{4pt}
	\begin{tabular}{lrr|rr|rr|rr|rr|rr}
		\tophline
		&\multicolumn{2}{c|}{Simulations}& \multicolumn{6}{c|}{QRNN-single} & \multicolumn{2}{c|}{QRNN-all} & \multicolumn{2}{c}{Pure filtering}\\
		\cline{2-13}
		%		\hline
		&   Clear-sky &   All-sky &  \multicolumn{2}{c|}{89+150\,GHz} & \multicolumn{2}{c|}{89+150+118\,GHz} & \multicolumn{2}{c|}{150\,GHz} & \multicolumn{2}{c|}{89+150+183\,GHz}& SI & B183\\		
		&			   &			& All & Pred. (5\,K) & All & Pred. (5\,K) & All & Pred. (5\,K)  & All & Pred. (5\,K)&&\\
		\middlehline
Bias     &  0.00 & $-$0.84 &$-$0.10 &$-$0.09 &$-$0.05 &$-$0.04 &$-$0.11 &$-$0.10 &$-$0.10 &$-$0.09 & 0.24  &$-$0.52\\
MAE      &  0.80 &   1.45 &  0.89 &  0.87 &  0.90 &  0.88 &  0.90 &  0.88 &  0.62 &  0.60 & 0.92  & 1.15\\
STD      &  1.00 &   3.73 &  1.20 &  1.16 &  1.21 &  1.16 &  1.22 &  1.18 &  0.91 &  0.85 & 1.26  & 1.86\\
Skewness &$-$0.02 &$-$12.72 &$-$1.17 &$-$1.00 &$-$1.06 &$-$0.90 &$-$1.16 &$-$1.04 &$-$1.78 &$-$1.71 &-1.95  &$-$3.45\\
Rejection& -	 &- 	  &-	  & 3.3\,\% &- 	  & 3.4\,\% &-     & 3.2\,\% &-     & 3.3\,\% & 28.8\,\%& 3.5\,\%\\
\bottomhline
	\end{tabular}
\end{table*}

@@

The three experiments were also performed for the other four 183\,GHz channels, and a similar performance was obtained (not shown). The positive effect of 118\,GHz was slightly higher for MWHS-2 channel 15, but for others, no notable effect was observed. In view of negligible performance differences between the three experiments, we consider the combination 89+150\,GHz to be optimal. The results for other channels with this experiment are provided in Sect.~\ref{sec:mwhs_others}.

>>>>

In this study, we approach the cloud filtering task from a new angle. The basic idea
is to derive an estimate of the corresponding noise-free clear-sky (NFCS) value
(i.e.\ the radiance that would have been measured in absence of noise and
hydrometeors). This is done for each channel separately and by only using the measurements, although the scheme is demonstrated in the study by using simulated observations. Not only a best estimate is provided, but also a case-specific uncertainty. This information could be used as a pure filter, by rejecting data where the correction exceeds some threshold value. However, even better is to replace the original value with the predicted NFCS value when forming the clear-sky dataset. We denote this approach as cloud correction.  It is shown below that a basically bias free cloud correction can be obtained. This feature also removes the need for defining threshold values, as long as the retrieval or assimilation system can incorporate the uncertainty of the corrected value. As also will be shown, the uncertainty for originally clear-sky data is determined
by noise, but the uncertainty increases with magnitude of correction.
Accordingly, the cloud correction approach permits the full weight of
clear-sky data to be preserved.

@@

The main focus of this study is the potential of this cloud-correction
method using sub-millimeter (sub-mm) observations, which will become available
operationally with the launch of the Ice Cloud Imager \citep[ICI,][]{eriksson:towar:20} on board the next generation of European Organisation for the Exploitation of Meteorological Satellites Polar System - Second Generation (EUMETSAT EPS-SG). Additionally, we demonstrate the feasibility of the approach based on 89 and 150\ GHz channels \citep[following][]{geer2015scatteringindex}, which are available on several sensors extant today. The focus
on sub-mm channels is motivated by several reasons. First, the higher
frequencies are more sensitive to scattering effects from smaller
hydrometeors and are thus expected to provide greater sensitivity to high altitude cirrus clouds. For example, in some cloudy situations the
cloud impact at 183\,GHz may be of the order of thermal noise and modelling uncertainties,
while the impact at 325\,GHz is significant enough to provide sufficient signal to noise for identifying cloud. Second, the proposed
cloud correction methods allow integration of ICI sub-mm observations in
clear-sky DA schemes with no further modifications, thus providing a simple
way to make use this novel data source as soon as it becomes available.

@@

\section{Data and methods}
\label{data_methods}
%
\subsection{Satellite Instruments}
%
\subsubsection{ MicroWave Humidity Sounder-2}
%
%t
\begin{table}[t]
	\caption{Specifications of MWHS-2 channels relevant to this study.}
	\label{tab:specifications_MWHS2}	
	\begin{tabular}{crrr}
		\tophline
		Channel & Frequency 	& Bandwidth & NE$\Delta$T \\
		& [GHz]			& [MHz]		& [K]		\\
		\middlehline
		1	&	89.0   		  & 1500			&	1.0	\\
		6	&	118.75±1.1    & \phantom{0}200 	&	1.6\\
		7	&	118.75±2.5    & \phantom{0}200 	&	1.6\\
		10	&	150.0         & 1500 			&	1.0 \\
		11	&	183.31±1.0      & \phantom{0}500  &	1.0 \\
		12  & 	183.31±1.8    & \phantom{0}700 	&   1.0\\
		13  & 	183.31±3.0      & 1000    		&	1.0	\\
		14  & 	183.31±4.5    & 2000    		&	1.0\\
		15  & 	183.31±7.0      & 2000  			&	1.0  \\
		\bottomhline
	\end{tabular}
	\belowtable{} % Table Footnotes
\end{table}
The MicroWave Humidity Sounder 2 (MWHS-2) is an instrument on two current satellites in the FengYun-3 series, FY-3C and FY-3D. MWHS-2 is a cross track scanning microwave radiometer and measures 15 frequencies in the range 89--191\,GHz. 89\,GHz and 150\,GHz are window channels, five humidity sounding channels are centered around 183\,GHz, and eight temperature sounding channels are centered on the 118\,GHz oxygen absorption line. The five humidity sounding channels are similar to ATMS. Observations from MWHS-2 are routinely assimilated in all-sky conditions at the European Centre for Medium-Range Weather Forecasts (ECMWF) with demonstrable positive impact on forecast performance \citep{duncan2020MWHS}. The channels relevant to this study are described in Table 1. It should be noted that the NE$\Delta$T values in the table are according to pre-launch specifications and not measured NE$\Delta$T values.

For the demonstration of the study, MWHS-2 simulations from the ECMWF model background are used. Actual measurements are not taken into account. The requisite data was obtained from ECMWF. More details are described in Sect.~\ref{simulations}.

@@

\subsection{Simulations}
%
\begin{figure}[t]
	\centering
	\includegraphics[width = 70mm]{Figures/fig01.pdf} 
	\caption{Probability distribution functions (PDFs) of simulated and observed brightness temperatures for MWHS-2 channel 14. The data covers latitude range $60^{\degree}$\,S to $60^{\degree}$\,N, and satellite zenith angle less than $7.5^{\degree}$.}
	\label{fig:distribution_OB_mwhs14}	
\end{figure}
\label{simulations}
MWHS-2 simulated radiances during the period June--July 2020 are sourced from ECMWF. In the current version of the ECMWF Integrated Forecasting System (IFS), cycle 47R1 \citep{IFS47R1chap1}, clear-sky and all-sky radiative transfer are performed simultaneously for monitoring purposes, despite all humidity sounders being assimilated via all-sky exclusively. These side by side radiative transfer calculations on a large variety of model scenes provides an ideal dataset for comparing radiances with and without cloud effects. Out of all the available observations during the period, we use data for the latitudinal range: $60^{\degree}$\,S to $60^{\degree}$\,N and satellite zenith angle, less than $7.5^{\degree}$. With this filter, we have approximately 290\,000 cases. Figure~\ref{fig:distribution_OB_mwhs14} shows the histogram of background and bias corrected observations for MWHS-2 channel 14. The part of the distribution matching clear-sky conditions shows a good agreement between the background and the observations. The main deviations in the distributions arise from the hydrometeor scattering. With limited scope of particle size and shape variation in current NWP microphysical schemes, the true cloud variability in radiance space is likely underestimated, though this is but one factor among many when it comes to the challenge of modelling clouds.

@@

The simulations are split into training and testing datasets. The training dataset is used to train the machine learning model, while the testing dataset is used to evaluate the trained model. The construction and details of the model are described in Sect.~\ref{sec:QRNN}. For MWHS-2, 220\,000 simulations are randomly selected as training dataset, while 70\,000 are used for testing. For ICI, 175\,000 cases are randomly picked to form the training set. The remaining 45\,000 are used for testing. We select a smaller database for SMS. 120\,000 simulations are used for training and the remaining 23\,000 for testing. We assume that SMS can be handled by smaller database due to lesser number of channels involved.

@@

QRNN's are trained to minimize the mean of the sum of the quantile loss functions,
%
\begin{align}
\mathcal{L}_\tau(y_\tau, y) &=
\begin{cases}
\tau|y - y_\tau|, & y_\tau < y \\ (1 - \tau)|y_\tau - y|, & \text{otherwise}
\\
\end{cases}
\end{align}
%
for all selected quantile fractions, where $y_\tau$ is the predicted
quantile and $y$ the reference value from the training or test data. The
quantile loss is also used in this study as a performance criterion for the tuning of
the hyper-parameters of the QRNN (see Appendix~\ref{appendix:hyperparamter}).  In
addition to the quantile loss, also the Continuously Ranked Probability Score
(CRPS) is considered. Given a predicted CDF
$F$ and the reference value $y$, the CRPS is defined as
%
\begin{align}
\text{CRPS}(F, y) = \int_{-\infty}^{\infty} \left (F(y') - \mathbf{I}_{y \leq y'} \right)^2\: dy',
\end{align}
%
where $\mathbf{I}_{y \leq y'}$ is the indicator function taking the value $1$ when the condition
$y \leq y'$ is true and $0$ otherwise.
To compute the CRPS for a prediction from a QRNN, the predicted quantiles are
used to derive a piece-wise linear approximation of the CDF of the predicted
distribution. Note that CRPS is only used to evaluate hyper-parameter tuning.

@@

\subsection{Evaluation metrics}
\label{sec:validation}
\begin{figure}[t]
	\centering
	\includegraphics[height=70mm]{Figures/fig02.pdf} 
	\caption{Examples showing the predicted quantiles of the conditional distribution of $\ynfcs$ }
	\label{fig:posterior_distribution_I1V}	
\end{figure}
QRNN predictions are posterior probability distribution of $\ynfcs$ described over the chosen quantiles. In order to facilitate the interpretation of results, examples of QRNN outputs are shown in Fig.~\ref{fig:posterior_distribution_I1V}. These examples illustrate the predicted quantiles for three different cases. The quantiles provide a quantification of the prediction uncertainty through a probabilistic upper and lower bound for each case. This is in contrast with other conventional correction/filtering methods, which give out only point estimates. However, for most applications only a single point estimate is required. In Bayesian analysis, usually the posterior mean or posterior median are selected as point estimates. In this study, we chose the posterior median as the best estimate for $\ynfcs$. To analyse the ability of QRNN in correctly predicting the point estimate, deviation of the median value from the corresponding true value ($\yonfcs$) is evaluated using common performance indicators like bias, mean absolute error (MAE) and standard deviation (STD). The asymmetry of error distributions around their mean is also calculated through the measure of skewness. For a univariate dataset of length $N$, the Fisher-Pearson coefficient of skewness is defined as: 
\begin{equation}
g_1 = 	\frac{\sqrt{N(N-1)}}{N-2} \frac{\sum_{i = 1}^{N}(Y_i - \bar{Y})^3/N}{\sigma^3} \,,
\end{equation}
where $\bar{Y}$ and $\sigma$ are mean and standard deviation of the deviations, respectively.

@@

\subsubsection{QRNN-single applied to MWHS-2 channel 14} 
\begin{figure}[t]
	\centering
	\includegraphics[width = 70mm]{Figures/fig03.pdf} 
	\caption{The distribution of point estimates (``Predicted'') obtained from QRNN-single 89+150\,GHz for MWHS-2 channel 14. The corresponding distributions for all-sky and clear-sky simulations are also shown.}
	\label{fig:distribution_predicted_mwhs14}	
\end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width = 70mm]{Figures/fig04.pdf} 
	\caption{The error distribution for deviations of point estimates from NFCS simulations. The results are from QRNN-single experiment 89+150\,GHz and MWHS-2 channel 14. Noise is also plotted for reference. The label ``All-sky'' represents the all-sky simulations, ``Predicted (All)'' denotes the predicted point estimates. The error distribution achieved with scattering index (SI) filtering is also shown (Filtered (SI)). }
	\label{fig:error_distribution_mwhs14}	
\end{figure}
\begin{table*}[t]
	\caption{The error statistics for deviations of point estimates from NFCS simulations. Results are for different QRNN experiments for MWHS-2 channel 14 (see Sect.~\ref{sec:QRNN_expt_MWHS}). The statistics for all-sky and clear-sky simulations are also provided. The label ``All'' denotes the entire dataset of predicted point estimates, while ``Pred. (5\,K)'' refers to the predicted point estimates but where cases with cloud correction greater than 5\,K are excluded. The last two columns show the statistics obtained after filtering cloudy cases according to scattering index (SI) and scheme by \citet{buehler:aclou:07} (B183). Bias, MAE, STD are in K, skewness is dimensionless.}
	\label{tab:error_statistics_mwhs_14}
	\setlength{\tabcolsep}{4pt}
	\begin{tabular}{lrr|rr|rr|rr|rr|rr}
		\tophline
		&\multicolumn{2}{c|}{Simulations}& \multicolumn{6}{c|}{QRNN-single} & \multicolumn{2}{c|}{QRNN-all} & \multicolumn{2}{c}{Pure filtering}\\
		\cline{2-13}
		%		\hline
		&   Clear-sky &   All-sky &  \multicolumn{2}{c|}{89+150\,GHz} & \multicolumn{2}{c|}{89+150+118\,GHz} & \multicolumn{2}{c|}{150\,GHz} & \multicolumn{2}{c|}{89+150+183\,GHz}& SI & B183\\		
		&			   &			& All & Pred. (5\,K) & All & Pred. (5\,K) & All & Pred. (5\,K)  & All & Pred. (5\,K)&&\\
		\middlehline
Bias     &  0.00 & $-$0.84 &$-$0.10 &$-$0.09 &$-$0.05 &$-$0.04 &$-$0.11 &$-$0.10 &$-$0.10 &$-$0.09 & 0.24  &$-$0.52\\
MAE      &  0.80 &   1.45 &  0.89 &  0.87 &  0.90 &  0.88 &  0.90 &  0.88 &  0.62 &  0.60 & 0.92  & 1.15\\
STD      &  1.00 &   3.73 &  1.20 &  1.16 &  1.21 &  1.16 &  1.22 &  1.18 &  0.91 &  0.85 & 1.26  & 1.86\\
Skewness &$-$0.02 &$-$12.72 &$-$1.17 &$-$1.00 &$-$1.06 &$-$0.90 &$-$1.16 &$-$1.04 &$-$1.78 &$-$1.71 &-1.95  &$-$3.45\\
Rejection& -	 &- 	  &-	  & 3.3\,\% &- 	  & 3.4\,\% &-     & 3.2\,\% &-     & 3.3\,\% & 28.8\,\%& 3.5\,\%\\
\bottomhline
	\end{tabular}
\end{table*}

@@

The three experiments were also performed for the other four 183\,GHz channels, and a similar performance was obtained (not shown). The positive effect of 118\,GHz was slightly higher for MWHS-2 channel 15, but for others, no notable effect was observed. In view of negligible performance differences between the three experiments, we consider the combination 89+150\,GHz to be optimal. For other channels, the results with 89+150\,GHz experiment are provided in Sect.~\ref{sec:mwhs_others}.

\subsubsection{Comparison of QRNN-all and QRNN-single}
%
%f
\begin{figure*}[t]
	\centering
	\includegraphics[width=0.65\textwidth]{Figures/fig05.pdf} 
	\caption{ The triangular error correlation matrix obtained from (a) QRNN-single and (b) QRNN-all for MWHS-2. The label ``Clear'' represents cases with cloud impact less than 2\,K.}
	\label{fig:correlations_mwhs}	
\end{figure*}
To assess the differences between the capabilities of QRNN-all against QRNN-single, we  compare the error statistics obtained for 89+150\,GHz and 89+150+183\,GHz for channel 14.  Table~\ref{tab:error_statistics_mwhs_14} also shows the error statistics for the experiment QRNN-all. In comparison to QRNN-single, we obtain almost similar error bias with QRNN-all, but the MAE and standard deviation reduce by almost 30\,\% and 24\,\% respectively. However, the negative tail becomes more prominent. The low standard deviation, but strong negative tail indicates that the narrow spread is a consequence of correction of noise in clear-sky cases. Since a majority of the cases are clear-sky, their impact dominates the whole statistics. In order to probe the positive effect of QRNN-all, we also estimate the errors for all cases with cloud correction greater than 5\,K (table not shown). For such cases,  QRNN-all has slightly better accuracy than QRNN-single. The bias in QRNN-all and standard deviation is $-$0.53\,K and 1.93\,K, respectively, in comparison to $-$0.61\,K and 2.04\,K as observed in QRNN-single. Thus, the concurrent use of all 183\,GHz channels can provide additional information on cloud structures to QRNN.
